An Automatic Verification Framework for Software Configurations

### 2016-05-09 OSDI/intro.tex
config: intro

To overcome these obstacles, researchers have proposed approaches based on
a statistical analysis and learning%
~\cite{wang04automatic, zhang14encore, yuan11context}
that try to infer the rules and policies 
how configuration files are constructed.
Rather than explicitly specifying entries' types or rules, 
these efforts are focused on learning policies from a sample dataset.
The learned rules are usually constructed along the following way: 
for every entry in a configuration file, 
they check if it deviates from a ``typical'' value, \ie, 
a value computed from a large training set 
consisting of configuration files.
If the entry is significantly different that the typical value, 
they suspect that it could be a potential configuration error.
The downside of these approaches is that these learning approaches 
are limited to simplistic configuration errors, 
such as type errors and syntax errors, or they 
heavily rely on template-based inference~\cite{zhang14encore}. 
As we pointed out earlier, 
since configuration files are not written in a typed language 
with a fixed syntax,
type errors and syntax errors are relatively rare and easy to detect. 
However, many sophisticated configuration errors, 
which are difficult to template in practice, 
cannot be detected by this way. 
As an illustration of such an error consider the ordering errors, 
which happens when some entries are inserted in a wrong order. 
For example, if in a PHP configuration file 
an entry {\tt extension = mysql.so} appears 
before {\tt extension = recode.so},  
it would lead to a crash error, where the Apache server cannot start 
due to the segmentation fault error. The correct ordering 
should be {\tt extension = recode.so} before 
{\tt extension = mysql.so}~\cite{yin11anempirical}.
These types of errors cannot be detected by existing
learning efforts, 
since it is hard to build a corresponding template~\cite{xu15systems}: 
we would need to capture ordering relations of all the entries. 
Some of them can appear in an arbitrary ordering, 
and the resulting templates would be too large 
and not efficient for a practical use.

>>>>

To overcome these obstacles, researchers have proposed approaches based on
a statistical analysis and learning%
~\cite{wang04automatic, zhang14encore, yuan11context}
that try to infer the rules and policies 
how configuration files are constructed.
Rather than explicitly specifying entries' types or rules, 
these efforts are focused on learning policies from a sample dataset.
The learned rules are usually constructed along the following way: 
for every entry in a configuration file, 
they check if it deviates from a ``typical'' value, \ie, 
a value computed from a large training set 
consisting of configuration files.
If the entry is significantly different that the typical value, 
they suspect that it could be a potential configuration error.

The downside of these approaches is that their learning approaches 
are limited to simplistic configuration errors, 
such as type errors and syntax errors, or they 
heavily rely on template-based inference~\cite{zhang14encore}. 
As we mentioned earlier, 
because configuration files are not written in a typed language 
with a fixed syntax,
type errors and syntax errors are relatively rare and easy to detect. 
However, many sophisticated configuration errors, 
which are difficult to template in practice, 
cannot be detected by this way. 
As an illustration of such an error consider the ordering errors, 
which happens when some entries are inserted in a wrong order. 
For example, if in a PHP configuration file 
an entry {\tt extension = mysql.so} appears 
before {\tt extension = recode.so},  
it would lead to a crash error, where the Apache server cannot start 
due to the segmentation fault error. The correct ordering 
should be {\tt extension = recode.so} before 
{\tt extension = mysql.so}~\cite{yin11anempirical}.
These types of errors cannot be detected by existing
learning efforts, 
since it is hard to build a corresponding template~\cite{xu15systems}: 
we would need to capture ordering relations of all the entries. 
Some of them can appear in an arbitrary ordering, 
and the resulting templates would be too large 
and not efficient for a practical use.
